### 2023-12-05 main.tex
ll

@@

\section{Correlations and steady state  for the integrable chain}\label{sectionIntegrabiliy}
In this section we combine duality, the $gl(N)$ invariance and the matrix product ansatz (MPA) to charaterize the non-equilibrium steady state for the integrable version of the multispecies stirring process, defined in Section~\ref{integrableChain-duality}. 
As it will turn out, the combination of the $gl(N)$ invariance  and the MPA allows to determine a closed formula for the absorption probabilities and thus (using Corollary~\ref{Corolollary-ABS_Corr-abstract}) for the correlations
and (using Corollary~\ref{Corollary-NESS-ABS}) for the probability mass-function of the non-equilibrium steady state.
We start by recalling the formulation of the MPA  and then we explain our strategy.

\subsection{Matrix product ansatz for the non-equilibrium steady state}
The matrix product ansatz for the multispecies stirring process has been formulated in \cite{vanicat2017exact}, here we briefly recall the main steps.
 Denoting by $|\Psi(t)\rangle$ the column vector that encodes the probability distribution of the chain with Hamiltonian \eqref{hamiltonian} at time $t\geq 0$, its evolution equation is given by 
 the master equation
\begin{equation}
    \frac{d|{\Psi}(t)\rangle}{dt}=H|{\Psi}(t)\rangle\dt
\end{equation}
This Markov chain is irreducible and positive recurrent, therefore there exists a unique stationary measure, that will be reached when time goes to infinity, regardless of the initial configuration. 
We denote by $|\Psi\rangle$ the column vector that gives the stationary distribution (non-equilibrium steady state). This vector is the right eigenvector with vanishing eigenvalue of $H$, i.e. it solves 
\begin{equation}\label{definition-SteadyStateH}
	H|\Psi\rangle =0\dt
\end{equation}
The MPA states the following
\begin{equation}
	|\Psi\rangle=\frac{1}{Z_{L}}\langle W|\begin{pmatrix}
		X_{1}\\
		\vdots\\
		X_{N}
	\end{pmatrix}\otimes \ldots\otimes \begin{pmatrix}
		X_{1}\\
		\vdots\\
		X_{N}
	\end{pmatrix}|V\rangle
\end{equation}
with the normalization 
\begin{equation}
	Z_{L}=\langle W|(X_{1}+\ldots +X_{N})^{L}|V\rangle\dt
\end{equation}
Here the operators $(X_{a})_{a\in \{1,\ldots,N\}}$ fulfil the commutators
\begin{equation}\label{bulk}
	\left[X_{a},X_{b}\right]=(\alpha_{a}-\beta_{a})X_{b}-(\alpha_{b}-\beta_{b})X_{a}%\qquad\forall a,b=1,\ldots,N
\end{equation}
and their action on the boundary vectors are
\begin{equation}\label{leftBoundary}
	\langle W|\left(\alpha_{a}(X_{1}+\ldots+X_{N})-X_{a}\right)=(\alpha_{a}-\beta_{a})\langle W|%\qquad\forall a=1,\ldots,N\co
\end{equation}
\begin{equation}\label{rightBoundary}
	\left(\beta_{a}(X_{1}+\ldots+X_{N})-X_{a}\right)|V\rangle=-(\alpha_{a}-\beta_{a})|V\rangle%\qquad\forall a=1,\ldots,N\dt
\end{equation}
Without loss of generality, we further assume that $\langle W|V\rangle=1$. 
\begin{remark} Only $N-1$ of the $N$ equations \eqref{leftBoundary}  are independent. This can be seen by summing them over the species $a\in \{1,\ldots,N\}$, i.e.
	\begin{equation}
		\sum_{a=1}^{N}	\langle W|\left(\alpha_{a}(X_{1}+\ldots+X_{N})-X_{a}\right)=0,%\sum_{a=1}^{N}(\alpha_{a}-\beta_{a})\langle W|=0
	\end{equation}
	and using  \eqref{ratesConditions}.
 Similarly for the right boundary  \eqref{rightBoundary} there are only  $N-1$ independent equations. \end{remark} 
The MPA gives an abstract form of the non-equilibrium steady state in terms of an algebra of operators. However, the computation of  correlations are in general involved.

@@

 The idea is summarized in the following scheme. 
 We define a sequence of similarity transformation such that 
 \begin{equation}
 	H\;\xleftrightarrow{S_{1}}\;H^{'}\;\xleftrightarrow{S_{2}}\;H^{''}
 \end{equation} 
 where $H^{'}= S_{1} H S_{1}^{-1} $ has both boundary terms in a triangular form, and $H^{''} = S_{2}H' S_{2}^{-1}$ has the left boundary in a triangular form and the right boundary is diagonal. Using these transformations the commutators \eqref{bulk} and the action on the boundary vectors \eqref{leftBoundary}, \eqref{rightBoundary} simplify significantly. More precisely for the components of $\tilde X=S_2S_1 X$ we obtain the bulk relations
\begin{equation}\label{commutationsBula2}
	\left[\Xt_{a},\Xt_{N}\right]=(\alpha_{a}-\beta_{a})\Xt_{N}\dt %\forall a\in \{1,\ldots,N-1\}\dt
\end{equation}
for $a=1,\ldots,N-1$. 
At the boundaries 
\begin{equation}\label{commLEFT2}
	\langle W|\left((\alpha_{a}-\beta_{a})\Xt_{N}-\Xt_{a}\right)=(\alpha_{a}-\beta_{a})\langle W|%\qquad\forall a=1,\ldots,N-1
	\co \qquad 
	\Xt_{a} |V\rangle= (\alpha_{a}-\beta_{a})|V\rangle%\qquad\forall a=1,\ldots,N-1
	\,.
\end{equation} 
where again we have  $a=1,\ldots,N-1$.   As a consequence, the ground state $|\Psi^{''}\rangle$ of $H^{''}$ can be written exactly in closed-form. Finally, reversing the transformations we retrieve $|\Psi\rangle$, i.e. the vector whose components are the probabilities of a certain configuration of the process in the non-equilibrium steady state.
 The first transformation $S_{1}$ is closely related to the duality matrix and we will see that $H^{'}$ is $\widetilde{H}^{T}$, up to the extra-site term described by the bosonic creation operator in \eqref{siteDualHamiltonian}. Therefore, $H^{'}$ is not stochastic, however it turns out that the components of its eigenvector with zero eigenvalue $|\Psi^{'}\rangle$ are the correlations in the non-equilibrium steady state. 
 %The second transformation $S_{2}$ diagonalizes the right boundary. Finally, the composition  $S_{2} S_{1}$ allows to simplify the commutators of the MPA algebra. 
\subsection{Correlations in the non-equilibrium steady state}\label{subsection-exact}
In this section we write a formula for the stationary non-equilibrium steady state correlations between $m$- points of the chain.
\begin{theorem}[Correlations in the non-equilibrium steady state]\label{thm-correlations}
%Consider $m\in \{1,\ldots,L\}$ points with coordinates given by $(x_{1},\ldots,x_{m})$, such that $x_{k}<x_{k+1}$ $\forall k\in \{1,\ldots,m-1\}$
%and consider $m$ species $a_{k}\in \{1,\ldots,N-1\}$. 
Let $m\in \{1,\ldots,L\}$ and consider $m$ sites $1 \le x_{1} < x_2 < \ldots < x_m \le L $ and
$m$ species $a_{k}\in\{1,\ldots,N-1\}$  with $k=1,2,\ldots, m$. Then the $m$-point correlations with respect to the non-equilibrium steady state measure are given by 
\begin{equation}\label{exactCorrelations}
\mathbb{E}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=a_{k}\}}\right]\\=\sum_{t_{1},\ldots,t_{m}=0}^{1}\left(\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\right)\mathcal{P}_{x_{1},\ldots,x_{m}}(t_{1},\ldots,t_{m})
\end{equation}
where
\begin{equation}\label{abs-probabilities}
	\mathcal{P}_{x_{1},\ldots,x_{m}}(t_{1},\ldots,t_{m})=\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}f(c_{1},\ldots,c_{m})\prod_{j=1}^{m}(-1)^{c_{j}-t_{j}}g_{j}(x_{j},c_{j},\ldots,c_{m})
\end{equation}
with
\begin{equation}\label{powerCoeffNOspec}
	f(c_{1},\ldots,c_{m})=\frac{(L+1-\sum_{a=1}^{m}c_{a})!}{(L+1)!}
\end{equation}
and
\begin{equation}\label{powerCoeffSpecies}
	g_{j}(x_{j},c_{j},\ldots,c_{m})=\left(L+2-x_{j}-\sum_{k=j}^{m}c_{k}\right)^{c_{j}}\dt
\end{equation}
\end{theorem}

@@

\paragraph{Proof of formula \eqref{ResulsBasis}}  
We consider the vector with elements given by the operators of the MPA $(X_{1},\ldots,X_{N})$ and we act on it with the similarity transformation $S=S_{2}S_{1}$ obtaining new operators $(\Xt_{1},\ldots,\Xt_{N})$ that will satisfy simpler commutation relations. 
For the sake of notation we denote by
\begin{equation}
    \begin{pmatrix}
		X_{a}\\ 
		X_{N}
	\end{pmatrix}=\begin{pmatrix}
	    X_{1}\\
     \vdots\\
     X_{N}
	\end{pmatrix}\dt
\end{equation}
We define the transformed matrix product operators
\begin{equation}\label{Xtildes2b}
	\begin{pmatrix}
		\Xt_{a}\\ 
		\Xt_{N}
	\end{pmatrix} =S\begin{pmatrix}
		X_{a}\\X_{N}
	\end{pmatrix}=\begin{pmatrix} 
		X_{a}-\beta_{a}(X_{1}+\ldots+X_{N})\\
				X_{1}+\ldots +X_{N}\\
	\end{pmatrix}\dt
\end{equation}
We can also reverse the transformation by $S^{-1}$ and get back: 
\begin{equation}\label{Xes}
	\begin{pmatrix}
		X_{a}\\
		X_{N} 
	\end{pmatrix} =S^{-1}\begin{pmatrix}
		\widetilde{X}_{a}\\
		\widetilde{X}_{N}
	\end{pmatrix}=\begin{pmatrix}
		\Xt_{a}+\beta_{a}\Xt_{N}\\ 
		\beta_N\Xt_{N}-(\Xt_{1}+\ldots+\Xt_{N-1})
	\end{pmatrix}\dt
\end{equation}
Summing over $b\in \{1,\ldots,N\}$ in commutation relations \eqref{bulk} we have
\begin{equation} 
	\left[X_{a},\Xt_{N}\right]=(\alpha_{a}-\beta_{a})\Xt_{N}
\end{equation}
with $\widetilde{X}_{N}=\widetilde{X}_{1}+\ldots+\widetilde{X}_{N}$. 
Therefore, we obtain the commutation relations for $\Xt_{a}$ 
\begin{equation}\label{commutationsBula}
	\left[\Xt_{a},\Xt_{N}\right]=(\alpha_{a}-\beta_{a})\Xt_{N}\co
\end{equation}
cf.~\eqref{commutationsBula2}.
Moreover using \eqref{Xtildes2b} and \eqref{Xes}, the action of $\Xt_{a}$ on the boundary vectors are given by 
\begin{equation}\label{commLEFT}
	\langle W|\left((\alpha_{a}-\beta_{a})\Xt_{N}-\Xt_{a}\right)=(\alpha_{a}-\beta_{a})\langle W|
	\co
\end{equation}
\begin{equation}\label{commRIGHT}
	\Xt_{a} |V\rangle= (\alpha_{a}-\beta_{a})|V\rangle
	\co
\end{equation} 
cf.~\eqref{commLEFT2}.
Using the transformed operators $(\widetilde{X}_{a})_{a\in\{1,\ldots,N\}}$, the vector $|\Psi^{''}\rangle$ of the matrix product ansatz is written as
\begin{equation}\label{toDetermineTilde}
	|\Psi^{''}\rangle = \frac{1}{Z_{L}}\sum_{\bm{\tau}\in \Omega^{'}}\langle W|\prod_{x=1}^{L}\widetilde{X}_{\tau_{x}}
	|V \rangle \,|\bm{\tau}\rangle
\end{equation}
where the normalization is given by 
\begin{align}
		Z_{L}&=\langle W|(X_{1}+\ldots+X_{N})^{L}|V\rangle=\langle W|\widetilde{X}_{N}^{L}|V\rangle\dt
\end{align}

To determine the eigenvector \eqref{toDetermineTilde}, we compute the coefficient $\langle W|\prod_{x=1}^{L}\widetilde{X}_{\tau_{x}}
|V \rangle$ and the normalization $Z_{L}$. Using \eqref{commutationsBula} we have
\begin{equation}\label{UsefulRelation}
	\widetilde{X}_{a}\widetilde{X}_{N}=\widetilde{X}_{N}\left((\alpha_{a}-\beta_{a})+\widetilde{X}_{a}\right)\dt
\end{equation}
Fix $ a\in \{1,\ldots,N-1\}$ and arbitrary $ \ell,n\in \mathbb{N}$. By applying the above formula \eqref{UsefulRelation} we have
\begin{align}\label{usefulRelaton-many}
	\widetilde{X}_{a}^{n}\widetilde{X}_{N}^{\ell}&=
	\widetilde{X}_{N}^{\ell}\left(\widetilde{X}_{a}+\ell(\alpha_{a}-\beta_{a})\right)^{n}\dt
\end{align}

>>>>

\todo{but these are the correlations, no?}

@@

\section{Correlations and steady state  for the integrable chain}\label{sectionIntegrabiliy}
In this section we combine the matrix product ansatz (MPA) \cite{vanicat2017exact} and  the $gl(N)$ invariance of the process in the bulk, cf.~\eqref{symmetryH}, to exactly compute the correlations in the non-equilibrium steady state
 for the integrable version of the multispecies stirring process on a defined on a line segment, see Section~\ref{integrableChain-duality}. 
This allows further to determine the absorption probabilities and the probability mass-function of the non-equilibrium steady state in closed form.
We start by recalling the formulation of the MPA  and then we explain our strategy.

% In this section we combine duality, the $gl(N)$ invariance and the matrix product ansatz (MPA) to charaterize the non-equilibrium steady state for the integrable version of the multispecies stirring process, defined in Section~\ref{integrableChain-duality}. 
% As it will turn out, the combination of the $gl(N)$ invariance  and the MPA allows to determine a closed formula for the absorption probabilities and thus (using Corollary~\ref{Corolollary-ABS_Corr-abstract}) for the correlations
% and (using Corollary~\ref{Corollary-NESS-ABS}) for the probability mass-function of the non-equilibrium steady state.
% We start by recalling the formulation of the MPA  and then we explain our strategy.

\subsection{Matrix product ansatz for the non-equilibrium steady state}
The matrix product ansatz for the multispecies stirring process has been formulated in \cite{vanicat2017exact}, here we briefly recall the main steps.
 Denoting by $|\Psi(t)\rangle$ the column vector that encodes the probability distribution of the chain with Hamiltonian \eqref{hamiltonian} at time $t\geq 0$, its evolution equation is given by 
 the master equation
\begin{equation}
    \frac{d|{\Psi}(t)\rangle}{dt}=H|{\Psi}(t)\rangle\dt
\end{equation}
This Markov chain is irreducible and positive recurrent, therefore there exists a unique stationary measure, that will be reached when time goes to infinity, regardless of the initial configuration. 
We denote by $|\Psi\rangle$ the column vector that gives the stationary distribution (non-equilibrium steady state). This vector is the right eigenvector with vanishing eigenvalue of $H$, i.e. it solves 
\begin{equation}\label{definition-SteadyStateH}
	H|\Psi\rangle =0\dt
\end{equation}
The MPA states the following
\begin{equation}
	|\Psi\rangle=\frac{1}{Z_{L}} \langle \langle W|  \begin{pmatrix}
		X_{1}\\
		\vdots\\
		X_{N}
	\end{pmatrix}\otimes \ldots\otimes \begin{pmatrix}
		X_{1}\\
		\vdots\\
		X_{N}
	\end{pmatrix} |V\rangle\rangle 
\end{equation}
with the normalization 
\begin{equation}
	Z_{L}= \langle \langle W|  (X_{1}+\ldots +X_{N})^{L} |V\rangle\rangle \dt
\end{equation}
Here the operators $(X_{a})_{a\in \{1,\ldots,N\}}$ fulfil the commutators
\begin{equation}\label{bulk}
	\left[X_{a},X_{b}\right]=(\alpha_{a}-\beta_{a})X_{b}-(\alpha_{b}-\beta_{b})X_{a}%\qquad\forall a,b=1,\ldots,N
\end{equation}
and their action on the boundary vectors are
\begin{equation}\label{leftBoundary}
	 \langle \langle W|  \left(\alpha_{a}(X_{1}+\ldots+X_{N})-X_{a}\right)=(\alpha_{a}-\beta_{a}) \langle \langle W|  %\qquad\forall a=1,\ldots,N\co
\end{equation}
\begin{equation}\label{rightBoundary}
	\left(\beta_{a}(X_{1}+\ldots+X_{N})-X_{a}\right) |V\rangle\rangle =-(\alpha_{a}-\beta_{a}) |V\rangle\rangle %\qquad\forall a=1,\ldots,N\dt
\end{equation}
Without loss of generality, we further assume that $ \langle \langle W|  V\rangle=1$. 
\begin{remark} Only $N-1$ of the $N$ equations \eqref{leftBoundary}  are independent. This can be seen by summing them over the species $a\in \{1,\ldots,N\}$, i.e.
	\begin{equation}
		\sum_{a=1}^{N}	 \langle \langle W|  \left(\alpha_{a}(X_{1}+\ldots+X_{N})-X_{a}\right)=0,%\sum_{a=1}^{N}(\alpha_{a}-\beta_{a}) \langle \langle W|  =0
	\end{equation}
	and using  \eqref{ratesConditions}.
 Similarly for the right boundary  \eqref{rightBoundary} there are only  $N-1$ independent equations. \end{remark} 
The MPA gives an abstract form of the non-equilibrium steady state in terms of an algebra of operators. However, the computation of  correlations are in general involved.

@@

 The idea is summarized in the following scheme. 
 We define a sequence of similarity transformation such that 
 \begin{equation}
 	H\;\xleftrightarrow{S_{1}}\;H^{'}\;\xleftrightarrow{S_{2}}\;H^{''}
 \end{equation} 
 where $H^{'}= S_{1} H S_{1}^{-1} $ has both boundary terms in a triangular form, and $H^{''} = S_{2}H' S_{2}^{-1}$ has the left boundary in a triangular form and the right boundary is diagonal. Using these transformations the commutators \eqref{bulk} and the action on the boundary vectors \eqref{leftBoundary}, \eqref{rightBoundary} simplify significantly. More precisely for the components of $\tilde X=S_2S_1 X$ we obtain the bulk relations
\begin{equation}\label{commutationsBula2}
	\left[\Xt_{a},\Xt_{N}\right]=(\alpha_{a}-\beta_{a})\Xt_{N}\dt %\forall a\in \{1,\ldots,N-1\}\dt
\end{equation}
for $a=1,\ldots,N-1$. 
At the boundaries 
\begin{equation}\label{commLEFT2}
	 \langle \langle W|  \left((\alpha_{a}-\beta_{a})\Xt_{N}-\Xt_{a}\right)=(\alpha_{a}-\beta_{a}) \langle \langle W|  %\qquad\forall a=1,\ldots,N-1
	\co \qquad 
	\Xt_{a}  |V\rangle\rangle = (\alpha_{a}-\beta_{a}) |V\rangle\rangle %\qquad\forall a=1,\ldots,N-1
	\,.
\end{equation} 
where again we have  $a=1,\ldots,N-1$.   As a consequence, the ground state $|\Psi^{''}\rangle$ of $H^{''}$ can be written exactly in closed-form. Finally, reversing the transformations we retrieve $|\Psi\rangle$, i.e. the vector whose components are the probabilities of a certain configuration of the process in the non-equilibrium steady state.
 The first transformation $S_{1}$ is closely related to the duality matrix and we will see that $H^{'}$ is $\widetilde{H}^{T}$, up to the extra-site term described by the bosonic creation operator in \eqref{siteDualHamiltonian}. Therefore, $H^{'}$ is not stochastic, however it turns out that the components of its eigenvector with zero eigenvalue $|\Psi^{'}\rangle$ are the correlations in the non-equilibrium steady state. 
 %The second transformation $S_{2}$ diagonalizes the right boundary. Finally, the composition  $S_{2} S_{1}$ allows to simplify the commutators of the MPA algebra. 
\subsection{Correlations in the non-equilibrium steady state}\label{subsection-exact}
In this section we write a formula for the stationary non-equilibrium steady state correlations between $m$- points of the chain.
\begin{theorem}[Correlations in the non-equilibrium steady state]\label{thm-correlations}
%Consider $m\in \{1,\ldots,L\}$ points with coordinates given by $(x_{1},\ldots,x_{m})$, such that $x_{k}<x_{k+1}$ $\forall k\in \{1,\ldots,m-1\}$
%and consider $m$ species $a_{k}\in \{1,\ldots,N-1\}$. 
Let $m\in \{1,\ldots,L\}$ and consider $m$ sites $1 \le x_{1} < x_2 < \ldots < x_m \le L $ and
$m$ species $a_{k}\in\{1,\ldots,N-1\}$  with $k=1,2,\ldots, m$. Then the $m$-point correlations with respect to the non-equilibrium steady state measure are given by 
\begin{equation}\label{exactCorrelations}
\mathbb{E}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=a_{k}\}}\right]\\=\sum_{t_{1},\ldots,t_{m}=0}^{1}\left(\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\right)\mathcal{P}_{x_{1},\ldots,x_{m}}(t_{1},\ldots,t_{m})
\end{equation}
where
\begin{equation}\label{abs-probabilities}
	\mathcal{P}_{x_{1},\ldots,x_{m}}(t_{1},\ldots,t_{m})=\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}f(c_{1},\ldots,c_{m})\prod_{j=1}^{m}(-1)^{c_{j}-t_{j}}g_{j}(x_{j},c_{j},\ldots,c_{m})
\end{equation}
with
\begin{equation}\label{powerCoeffNOspec}
	f(c_{1},\ldots,c_{m})=\frac{(L+1-\sum_{a=1}^{m}c_{a})!}{(L+1)!}
\end{equation}
and
\begin{equation}\label{powerCoeffSpecies}
	g_{j}(x_{j},c_{j},\ldots,c_{m})=\left(L+2-x_{j}-\sum_{k=j}^{m}c_{k}\right)^{c_{j}}\dt
\end{equation}
\end{theorem}

@@

\paragraph{Proof of formula \eqref{ResulsBasis}}  
We consider the vector with elements given by the operators of the MPA $(X_{1},\ldots,X_{N})$ and we act on it with the similarity transformation $S=S_{2}S_{1}$ obtaining new operators $(\Xt_{1},\ldots,\Xt_{N})$ that will satisfy simpler commutation relations. 
For the sake of notation we denote by
\begin{equation}
    \begin{pmatrix}
		X_{a}\\ 
		X_{N}
	\end{pmatrix}=\begin{pmatrix}
	    X_{1}\\
     \vdots\\
     X_{N}
	\end{pmatrix}\dt
\end{equation}
We define the transformed matrix product operators
\begin{equation}\label{Xtildes2b}
	\begin{pmatrix}
		\Xt_{a}\\ 
		\Xt_{N}
	\end{pmatrix} =S\begin{pmatrix}
		X_{a}\\X_{N}
	\end{pmatrix}=\begin{pmatrix} 
		X_{a}-\beta_{a}(X_{1}+\ldots+X_{N})\\
				X_{1}+\ldots +X_{N}\\
	\end{pmatrix}\dt
\end{equation}
We can also reverse the transformation by $S^{-1}$ and get back: 
\begin{equation}\label{Xes}
	\begin{pmatrix}
		X_{a}\\
		X_{N} 
	\end{pmatrix} =S^{-1}\begin{pmatrix}
		\widetilde{X}_{a}\\
		\widetilde{X}_{N}
	\end{pmatrix}=\begin{pmatrix}
		\Xt_{a}+\beta_{a}\Xt_{N}\\ 
		\beta_N\Xt_{N}-(\Xt_{1}+\ldots+\Xt_{N-1})
	\end{pmatrix}\dt
\end{equation}
Summing over $b\in \{1,\ldots,N\}$ in commutation relations \eqref{bulk} we have
\begin{equation} 
	\left[X_{a},\Xt_{N}\right]=(\alpha_{a}-\beta_{a})\Xt_{N}
\end{equation}
with $\widetilde{X}_{N}=\widetilde{X}_{1}+\ldots+\widetilde{X}_{N}$. 
Therefore, we obtain the commutation relations for $\Xt_{a}$ 
\begin{equation}\label{commutationsBula}
	\left[\Xt_{a},\Xt_{N}\right]=(\alpha_{a}-\beta_{a})\Xt_{N}\co
\end{equation}
cf.~\eqref{commutationsBula2}.
Moreover using \eqref{Xtildes2b} and \eqref{Xes}, the action of $\Xt_{a}$ on the boundary vectors are given by 
\begin{equation}\label{commLEFT}
	 \langle \langle W|  \left((\alpha_{a}-\beta_{a})\Xt_{N}-\Xt_{a}\right)=(\alpha_{a}-\beta_{a}) \langle \langle W|  
	\co
\end{equation}
\begin{equation}\label{commRIGHT}
	\Xt_{a}  |V\rangle\rangle = (\alpha_{a}-\beta_{a}) |V\rangle\rangle 
	\co
\end{equation} 
cf.~\eqref{commLEFT2}.
Using the transformed operators $(\widetilde{X}_{a})_{a\in\{1,\ldots,N\}}$, the vector $|\Psi^{''}\rangle$ of the matrix product ansatz is written as
\begin{equation}\label{toDetermineTilde}
	|\Psi^{''}\rangle = \frac{1}{Z_{L}}\sum_{\bm{\tau}\in \Omega^{'}} \langle \langle W|  \prod_{x=1}^{L}\widetilde{X}_{\tau_{x}}
	|V\rangle\rangle \,|\bm{\tau}\rangle
\end{equation}
where the normalization is given by 
\begin{align}
		Z_{L}&= \langle \langle W|  (X_{1}+\ldots+X_{N})^{L} |V\rangle\rangle = \langle \langle W|  \widetilde{X}_{N}^{L} |V\rangle\rangle \dt
\end{align}

To determine the eigenvector \eqref{toDetermineTilde}, we compute the coefficient $ \langle \langle W|  \prod_{x=1}^{L}\widetilde{X}_{\tau_{x}}
|V \rangle$ and the normalization $Z_{L}$. Using \eqref{commutationsBula} we have
\begin{equation}\label{UsefulRelation}
	\widetilde{X}_{a}\widetilde{X}_{N}=\widetilde{X}_{N}\left((\alpha_{a}-\beta_{a})+\widetilde{X}_{a}\right)\dt
\end{equation}
Fix $ a\in \{1,\ldots,N-1\}$ and arbitrary $ \ell,n\in \mathbb{N}$. By applying the above formula \eqref{UsefulRelation} we have
\begin{align}\label{usefulRelaton-many}
	\widetilde{X}_{a}^{n}\widetilde{X}_{N}^{\ell}&=
	\widetilde{X}_{N}^{\ell}\left(\widetilde{X}_{a}+\ell(\alpha_{a}-\beta_{a})\right)^{n}\dt
\end{align}

By taking the product over the sites $x$ from $1$ to $L$ we obtain 
\begin{equation}
	\prod_{x=1}^{L}\widetilde{X}_{\tau_{x}}=\widetilde{X}_{N}^{\sum_{x=1}^{L}\delta_{\tau_{x},N}}\prod_{x=1}^{L}\left(\widetilde{X}_{\tau_{x}}+(\alpha_{\tau_{x}}-\beta_{\tau_{x}})\sum_{j=x}^{L}\delta_{\tau_{x},N}\right)^{1-\delta_{\tau_{x},N}}\dt
\end{equation}
Multiplying by the boundary vectors and by using \eqref{commRIGHT} we have 
\begin{align}
	 \langle \langle W|  \prod_{x=1}^{L}\widetilde{X}_{\tau_{x}}
	|V \rangle=
	\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)^{1-\delta_{\tau_{x},N}} \langle \langle W|  \widetilde{X}_{N}^{\sum_{x=1}^{L}\delta_{\tau_{x},N}} |V\rangle\rangle  \dt
\end{align}
We now compute $ \langle \langle W|  \widetilde{X}_{N}^{\sum_{i=1}^{L}\delta_{\tau_{x},N}} |V\rangle\rangle $. For all $n\in \mathbb{N}$ we have that  
\begin{align}
	 \langle \langle W|  \widetilde{X}_{N}^{n} |V\rangle\rangle &= \langle \langle W|  \widetilde{X}_{N}\widetilde{X}_{N}^{n-1} |V\rangle\rangle = \langle \langle W|  \widetilde{X}_{N}^{n-1} |V\rangle\rangle  + \langle \langle W|  \frac{1}{(\alpha_{a}-\beta_{a})}\widetilde{X}_{a}\widetilde{X}_{N}^{n-1} |V\rangle\rangle \nonumber
	\\&=
	 \langle \langle W|  \widetilde{X}_{N}^{n-1} |V\rangle\rangle +\frac{1}{(\alpha_{a}-\beta_{a})} \langle \langle W|  \widetilde{X}_{N}^{n-1}\left(\widetilde{X}_{a}+(\alpha_{a}-\beta_{a})(n-1)\right) |V\rangle\rangle \nonumber
	\\&=
	 \langle \langle W|  \widetilde{X}_{N}^{n-1} |V\rangle\rangle +\left(n+1-1\right) \langle \langle W|  \widetilde{X}_{N}^{n-1} |V\rangle\rangle \nonumber
	\\&=
	\left(2+n-1\right) \langle \langle W|  \widetilde{X}_{N}^{n-1} |V\rangle\rangle \nonumber
	\\&=
	\frac{(1+n)!}{n!} \langle \langle W|  \widetilde{X}_{N}^{n-1} |V\rangle\rangle 
\end{align}
where in the second equality we used \eqref{usefulRelaton-many}. 
This leads to the recursion relation
\begin{align}
		 \langle \langle W|  \widetilde{X}_{N}^{n} |V\rangle\rangle =\frac{(1+n)!}{n!} \langle \langle W|  \widetilde{X}_{N}^{n-1} |V\rangle\rangle 
\end{align}
with $	 \langle \langle W|  \widetilde{X}_{N}^{0} |V\rangle\rangle =1$. 
Therefore, we obtain 
\begin{align}
	 \langle \langle W|  \widetilde{X}_{N}^{n} |V\rangle\rangle &=%\frac{\Gamma(2+n_{N})}{\Gamma(2+n_{N}-1)} \langle \langle W|  \widetilde{X}_{N}^{n_{N}-1} |V\rangle\rangle = \langle \langle W|  \widetilde{X}_{N}^{n_{N}} |V\rangle\rangle =\frac{\Gamma(2+n_{N})}{\Gamma(2+n_{N}-1)}\frac{\Gamma(2+n_{N}-1)}{\Gamma(2+n_{N}-2)} \langle \langle W|  \widetilde{X}_{N}^{n_{N}-2} |V\rangle\rangle \\&=
	\frac{(1+n)!}{n!}\frac{n!}{(n-1)!}\ldots \frac{3!}{2!}\frac{2!}{1!} \langle \langle W|  \widetilde{X}_{N}^{0} |V\rangle\rangle =
	(1+n)!\dt
\end{align}
By using this result we have that
\begin{equation}
	 \langle \langle W|  \prod_{x=1}^{L}\widetilde{X}_{\tau_{x}}
	|V\rangle\rangle=(1+\sum_{x=1}^{N}\delta_{\tau_{x},N})!\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)^{1-\delta_{\tau_{x},N}}\dt
\end{equation}
The normalization constant is then given by
\begin{align}
	Z_{L}&= \langle \langle W|  (X_{1}+\ldots+X_{N})^{L} |V\rangle\rangle = \langle \langle W|  \widetilde{X}_{N}^{L}|V|\rangle=
	(L+1)!\dt
\end{align}
Therefore, we write
\begin{equation}\label{resulEsteady}
	|\Psi^{''}\rangle= \sum_{\bm{\tau}\in \Omega^{'}}\frac{(1+\sum_{x=1}^{L}\delta_{\tau_{x},N})!}{(L+1)!}\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)^{1-\delta_{\tau_{x},N}}|\bm{\tau}\rangle\dt
\end{equation}
We observe that, for all $x$, we have
\begin{equation}
	\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)^{1-\delta_{\tau_{x},N}}=\frac{(1+\sum_{j=x+1}^{L}\delta_{\tau_{j},N})!}{(\sum_{j=x}^{L}\delta_{\tau_{j},N})!}\dt
\end{equation}
